---
title: "Documentation"
author: "Eva Katai"
date: "1/16/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Assignment

This is the final assignment of the Developing Data Products Course from Johns Hopkins University Data Science Specialization. This is the scope:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
1. Deploy the application on Rstudio's shiny server
1. Share the application link by pasting it into the provided text box
1. Share your server.R and ui.R code on github

## Dataset

The dataset is the standard mtcars. 

```{r dataset, echo = TRUE}
head(mtcars)
```

## Results

[the shiny webapp.](https://evafr.shinyapps.io/CourseProject/)

[github repository.](https://github.com/EvaFr/CourseProjectShinyApplication)

In the "Select variable for comparison" box please choose the suitable variable, 
and push the submit button.
After it, the program will draw the new model.

## Algorithm

The algorithm is the linear model function, that predicts the Miles Per Gallon based on the other  variable of the dataset. For example: 
"Number of cylinders" = "cyl"\
"Displacement" = "disp"\
"Gross horsepower" = "hp"\
"Rear axle ratio" = "drat"\
"Weight (lb/1000)" = "wt"\
"1/4 mile time" = "qsec"\
"V/S" = "vs"\
"Transmission" = "am"\
"Number of gears" = "gear"
    
## For example:

```{r algorithm, echo = TRUE}
fit <- lm(mpg ~ wt, mtcars)
with(mtcars,    {plot(mpg~wt)
                abline(fit, col=2)})
fit
```



